From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-28 Pi+/paper/ufin.tex
Add a diagram about UFin and enumerations

>>>>

\[
  \begin{tikzcd}
    \Fin[3]
    \arrow[""{name=0, anchor=center, inner sep=0}, "{f_{3}}", no head, loop, distance=4em, in=115, out=65]
    \arrow[""{name=0, anchor=center, inner sep=0}, "{f_{2}}", no head, loop, distance=8em, in=125, out=55]
    \arrow[""{name=1, anchor=center, inner sep=0}, "{f_{1}}"', no head, loop, distance=12em, in=135, out=45]
    \arrow["", "{h}", shorten <=3pt, shorten >=3pt, Rightarrow, no head, from=0, to=1]
  \end{tikzcd}
\]

We have $\Fin[3] & = \Set{0,1,2} \eqv \unit \sqcup (\unit \sqcup \unit)$ which fixes a particular enumeration of the
elements. Suppose we have a set $X = (\unit \sqcup \unit) \sqcup \unit$, it has the same cardinality as $\Fin[3]$, so it
is represented by the same 0-cell. But, $X$ can be made equivalent to $\Fin[3]$ in many different ways since there are
many bijections between them. One bijection is
$\Set{\inl(\inl(\ttt)) \mapsto 0, \inl(\inr(\ttt)) \mapsto 1, \inr(\ttt) \mapsto 2}$ which can be written in two
different ways by composing more primitive operations, $f_{1} = \assocrp$, or
$f_{2} = \swapp \compc \assoclp \compc \swapp$. Another bijection is
$\Set{\inl(\inl(\ttt)) \mapsto 1, \inl(\inr(\ttt)) \mapsto 2, \inr(\ttt) \mapsto 0}$ which is given by $f_{3} = \ldots$.
Since $f_{1}$ and $f_{2}$ produce the same enumeration of the elements of $X$, they are identified by a homotopy $h$
which is encoded in the 2-cell between them.
